Walling up Backdoors in Intrusion Detection Systems

### 2019-10-24 paper/paper.tex
Remove page numbers
Added CCS concepts/keywords

@@

\settopmatter{printfolios=true}
\maketitle

@@

In particular, we implemented the backdoor by incrementing the \gls{ttl} of a flow's first packet by one if its \gls{ttl} is smaller than 128 and decrementing it by 1 if is larger. This results in a tiny standard deviation of the \gls{ttl}
%(which would be otherwise undefined or zero)
as well as in changed max, min and mean.

>>>>

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002997.10002999</concept_id>
<concept_desc>Security and privacy~Intrusion detection systems</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257.10010293.10003660</concept_id>
<concept_desc>Computing methodologies~Classification and regression trees</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257.10010293.10010294</concept_id>
<concept_desc>Computing methodologies~Neural networks</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003083.10003014</concept_id>
<concept_desc>Networks~Network security</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Intrusion detection systems}
\ccsdesc[500]{Computing methodologies~Classification and regression trees}
\ccsdesc[500]{Computing methodologies~Neural networks}
\ccsdesc[300]{Networks~Network security}

\keywords{Network security, Deep Learning, Random Forests, Poisoning attack, Explainable AI, Pruning}

@@

%\settopmatter{printfolios=true}
\maketitle

@@

In particular, we implemented the backdoor by incrementing the \gls{ttl} of a flow's first packet by one if its \gls{ttl} is smaller than 128 and decrementing it by 1 if is larger. This results in a tiny standard deviation of the \gls{ttl}
%(which would be otherwise undefined or zero)
as well as in changed maximum, minimum and mean.
